%-------------------------
% Resume in Latex
% Author : Sarthak Thapliyal
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands 
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeProjectHeading}[2]{\item\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\\end{tabular*}\vspace{-7pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sarthak Thapliyal} \\ \vspace{1pt}
    \small +91-7895364210 $|$ \href{mailto:sarthakthapliyal007@gmail.com}{\underline{sarthakthapliyal007@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/sarthakthapliyal/}{\underline{linkedin.com/in/sarthakthapliyal}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graphic Era Hill University}{Dehradun, Uttarakhand}
      {Bachelor of Technology in Computer Science \& Engineering (Specialization in AI/ML)}{Aug.\ 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Object-Oriented Programming, Databases, Data Structures and Algorithms, Operating Systems, Computer Networks, Machine Learning}
      \resumeItemListEnd

    \resumeSubheading
      {Army Public School}{Dehradun, Uttarakhand}
      {Class XII - 71.6\%}{2022}

    \resumeSubheading
      {Army Public School}{Dehradun, Uttarakhand}
      {Class X - 83.2\%}{2020}

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C++, Java} \\
     \textbf{Frameworks \& Libraries}{: TensorFlow, Keras, PyTorch, Scikit-learn, Pandas, NumPy, OpenCV, NLTK} \\
     \textbf{Databases}{: MongoDB, MySQL} \\
     \textbf{Tools \& Platforms}{: Git, OpenAI API, Matplotlib}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{AI Chess Bot} $|$ \emph{Python, Chess Engine, Minimax Algorithm}}{2025}
        \resumeItemListStart
          \resumeItem{Developed an AI-powered chess engine in Python leveraging the python-chess library for real-time interactive gameplay.}
          \resumeItem{Implemented minimax algorithm with heuristic evaluation functions for intelligent move selection.}
          \resumeItem{Designed state management logic to track gameplay and ensure optimal performance.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Phishing Website \& Email Detector} $|$ \emph{Python, NLP, Machine Learning}}{2025}
        \resumeItemListStart
          \resumeItem{Built a machine learning-based phishing detection system in Python to identify malicious URLs and fraudulent emails.}
          \resumeItem{Implemented URL feature extraction, email header parsing, and NLP-based content classification.}
          \resumeItem{Achieved improved detection accuracy by applying supervised learning models and feature engineering techniques.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications \& Coding Profiles}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mastering Data Structures \& Algorithms using C and C++}{Online}
      {Instructor: Abdul Bari (60 hours)}{}
  \resumeSubHeadingListEnd

  \vspace{-6pt}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \small{\textbf{LeetCode}{: Solved 200+ problems in C++ covering data structures and algorithms.}}
    \item \small{\textbf{Competitive Programming}{: Active participant in weekly LeetCode contests and CodeForces Div-I/II rounds.}}
  \end{itemize}

%-------------------------------------------
\end{document}
